### 2022-06-08 src/text/5-summary-outlook.tex
Add reproducibility section

>>>>

\section{Reproducibility}
\label{sec:reproducibility}
One of the most important goals of the \gammapy project is to support open and
reproducible science results. Thus we decided to write this manuscript
completely openly and publish the Latex source code and associated
scripts in \url{https://github.com/gammapy/gammapy-v1.0-paper}.
This GitHub repository also documents the history of the creation
and evolution of the manuscript with time. To simplify the reproducibility
of this manuscript including figures and text, we relied on the tool
"showyourwork" (\todo{citation?}). This tool coordinates the building
process and software as well as data dependencies such, that the complete
manuscript can be reproduced with a single "make" command, after
downloading the source repository. See \todo{reference?} for detailed
instructions. Almost all figures in this manuscript provide a link
to a Pythin script, that was used to produce it. This means all
example analyses presented in Sec.\ref{sec:applications} link to
actuallly working Python source code.
